Paper notes

### 2019-08-16 paper_notes.Rmd
improved graphs

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
# Here functions that are used.

@@

 f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
   if (x < round(n*i_e,digits = 2)){
    U <- (x / round((n*i_e),digits = 2)) * S
     }else {
       U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
     }
   round(U,digits = 2)
     }
 }

@@

f_val <- function(e_w,ew_ng,M,i_v,S){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
      }
  round(U,digits = 2)
  }

@@

$$
U^i_e=
\begin{cases}
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
\\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
\end{cases}
$$

@@

```{r value graph function, fig.width=5,fig.height= 6, fig.align="center", include=TRUE, echo=FALSE}

@@

```{r ethnic utility individual-run,fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}

@@

i_e = 0.3
M = 1
S = 0
n = 7

@@

num_sim_col <- seq(0, 8, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

@@

report_E <- data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E)

@@

```{r ethnic_utility, moore neighborhood, include=TRUE, echo=FALSE}

@@

num_sim_col <- seq(0, 8, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)

print(report_E)

@@

```{r value_similarity, echo=FALSE }

@@

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

print(report_v)

@@

```{r logistic putting as in abm ethnic_weight, value_weight}

e_w <- 1
v_w <- 1-e_w

  value_difference <- seq(-1.0,1.0, by = 0.1)
  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  name_diff <- paste0("Note: "," Ethnic parameter = ", e_w*10," ;"," Value parameter = ", v_w*10, 
                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")

  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)

plot(value_difference,prob_choice, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
axis(2,at=seq(0.0, 1.0, by = 0.25))

```{r logistic in sequence, to test with parameters, to be deleted}

prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}

par_e <- 10
par_v <- 10 - par_e

  dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)

  value_difference <- seq(-1.0,1.0, by = 0.1)
  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)

  name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")

  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)

plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
axis(2,at=seq(0.0, 1.0, by = 0.25))

>>>>

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
# Here functions that are used.

@@

 #  f_eth <- function(i_e,M,x,n,S){
  #   if (x > n){
  #     U <- NA}else{
 #   if (x < round(n*i_e,digits = 2)){
  #    U <- (x / round((n*i_e),digits = 2)) * S
 #      }else {
 #      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
  #    }
#     round(U,digits = 2)
 #      }
#   }

  f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
     if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
      }else if (x > round((n*i_e),digits = 2)){
         U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
        }else{
     U <- 1}
        round(U,digits = 3)
      }
 }

@@

f_val <- function(e_w,ew_ng,M,i_v,S){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
      }
  round(U,digits = 3)
  }

@@

$$
U^i_e=
\begin{cases}
1, & \text{if} x =  n\times i_e, \\
\\
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
\\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x > n\times i_e 
\end{cases}
$$

@@

```{r value graph function, fig.width=6,fig.height=5, fig.align="center", include=TRUE, echo=FALSE}

@@

```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}

# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility

e_w <- 0.4
v_w <- 1-e_w

  value_difference <- seq(-1.0,1.0, by = 0.1)
#  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  title_cond_prob <- paste0("PROB ALT","Diff eth = ",d_u_e,"Ew = ",e_w*10,"Vw = ",v_w*10)

  report_prob <- na.omit(data.frame(value_difference,prob_choice))

  plot_report_prob <- ggplot(report_prob,aes(value_difference,prob_choice))

 final_prob <-  suppressWarnings(suppressMessages(
    plot_report_prob + geom_point() + theme_bw() + labs(x = "DIFF VAL",y = "Probability") + ggtitle(label = title_cond_prob) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted") 
  ))

  print(final_prob)

```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}

@@

i_e = 0.2
S = 0
M = 1
n = 6

@@

# num_sim_col <- seq(0, 8, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

# plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

@@

report_E <- na.omit(data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E))

title_cond <- paste0("Desired proportion = ", i_e,"; ", "S = ", S,"; " ,"M = ", M)

plot_report_E <- ggplot(report_E,aes(num_sim,Utility_E))

suppressWarnings(suppressMessages(
plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1))
))

@@

```{r value individual run,fig.width=5,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }

e_w <- 0.4
i_v <- 0.2
S  <- 1
M <- 0 #S regulates the left side of the slope, M the right side

# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
ew_agent <- rep(e_w,11)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
Mv <- rep(M,11)
Sv <- rep(S,11)
des_dist <- rep(i_v,11)

report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M = ",M,"S = ",S)

plot_report_V <- ggplot(report_V,aes(mean_ew_ng,Utility_V))

suppressWarnings(suppressMessages(
plot_report_V + geom_point() + theme_bw() + labs(x = "Mean ethnic weight j",y = "Value Utility j") + ggtitle(label = title_cond_V) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,1), breaks = seq(0,1,by = 0.1))
))

# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

knitr::kable(report_V,align="c") # much better printed visualization

# print(final_v)
# print(final_repV)

```{r ANNEX - ethnic_multiple_run, moore neighborhood, include=TRUE, echo=FALSE}

@@

#num_sim_col <- seq(0, n, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
#name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

#plot(num_sim_col,Utility_Es, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility", ylim = c(0,1),xlim = c(0,n),  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

#report_Es <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similars in j= ", seq(0, n, by = 1), "; Utility ij = ", Utility_Es)

#print(report_Es)

report_E <- na.omit(data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E))

title_cond <- paste0("Desired proportion = ", i_e,"; ", "S = ", S,"; " ,"M = ", M)

plot_report_E <- ggplot(report_E,aes(num_sim,Utility_E))

final_E <- suppressWarnings(suppressMessages(
plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1)) 
))

final_repE <- knitr::kable(report_E,align="c") # much better printed visualization

print(final_E)
print(final_repE)

@@

```{r ANNEX- value_similarity, echo=FALSE }

@@

# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
ew_agent <- rep(e_w,11)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
Mv <- rep(M,11)
Sv <- rep(S,11)
des_dist <- rep(i_v,11)

report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

plot_report_V <- ggplot(report_V,aes(mean_ew_ng,Utility_V))

final_v <- suppressWarnings(suppressMessages(
plot_report_V + geom_point() + theme_bw() + labs(x = "Mean ethnic weight j",y = "Value Utility j") + ggtitle(label = title_cond_V) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,1), breaks = seq(0,1,by = 0.1))
))

# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

final_repV <- knitr::kable(report_V,align="c") # much better printed visualization

print(final_v)
print(final_repV)

@@

```{r logistic in sequence, to test with parameters, to be deleted}
# 
# prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
# 
# for (d_u_e in seq (-1.0,1.0, by = 0.1)){
#   
# par_e <- 10
# par_v <- 10 - par_e
# 
# # d_u_e <- -1
# 
#   dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
# dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
# dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
# dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
# dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
# dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
# dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
# dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
# dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
# dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
# dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
# dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
# dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
# dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
# dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
# dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
# dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
# dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
# dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
# dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
# dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)
#   
#   value_difference <- seq(-1.0,1.0, by = 0.1)
#   prob_relocation <- seq(0.0, 1.0,  by = 0.1)
#   
#   prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)
#   
#   name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
#                       "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
#   
#   name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
#   
# plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
# axis(2,at=seq(0.0, 1.0, by = 0.25))

#}
